%-------------------------
% Resume in Latex
% Author : Mian Saad Tahir
% Repo: https://github.com/miansaadtahir/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Mian Saad Tahir} \\ \vspace{13pt}
    % 123 Street Name, Town, State 12345 \\ \vspace{1pt}
    
    \scriptsize \raisebox{-0.1\height}\faPhone\ +92 334-2241980 ~ \href{mailto:tahirsaad99@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{tahirsaad99@gmail.com}} ~ 
    \href{https://linkedin.com/in/miansadtahir/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/miansadtahir}}  ~
    \href{https://github.com/miansadtahir/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/miansadtahir}}  ~
    \href{https://miansaadtahir.netlify.app/}{\raisebox{-0.2\height}\faBriefcase\ \underline{miansaadtahir.netlify.app}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Engineering and Technology, Lahore}{Sep. 2023 -- May 2027}
      {Bachelor of Science in Computer Science}{CGPA: 3.5}
    \resumeSubheading
      {KIPS College, Lahore}{Nov. 2021 -- May 2023}
      {Intermediate in Computer Science}{Grade: A+}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Data Structures
                \item Algorithms Analysis
                \item Database Systems
                \item Computer Architecture
                \item Computer Networks
                \item Software Engineering
                \item Artificial Intelligence
                \item Information Security
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hack Secure}{Apr. 2025 -- May 2025}
      {Cyber Security Intern}{Remote}
      \resumeItemListStart
        \resumeItem{Performed comprehensive web application assessments using Nmap, Gobuster, and Wireshark to identify open ports,
misconfigured directories, and insecure data transmission.}
        \resumeItem{Exploited critical vulnerabilities including SQL Injection with sqlmap to enumerate databases and dump sensitive
data, and XSS to demonstrate stored and reflected script injection.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Price My Ride} -- \emph{Used car price estimator} $|$ \textbf{Flask, TensorFlow, Keras, Scikit-Learn}}{\href{https://github.com/MianSaadTahir/Price-My-Ride}{Source Code}}
          \resumeItemListStart
            \resumeItem{Developed a Flask web app that predicts used car prices using a custom-trained Deep Neural Network (DNN) model.}
            \resumeItem{Built a 3-layer DNN using TensorFlow and Keras with One-Hot Encoding and visualized key regression metrics.}
            \resumeItem{Prepared an IEEE-format research paper detailing the project’s methodology, experiments, evaluation, and results.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Threat Guard} -- \emph{Cybersecurity web app} $|$ \textbf{Flask, Python, SQLite, REST API}}{\href{https://github.com/MianSaadTahir/threat-guard}{Source Code}}
          \resumeItemListStart
            \resumeItem{Built a Flask app to scan URLs, files, and QR codes for malware using VirusTotal API and jsQR.}
            \resumeItem{Integrated breach detection through the HaveIBeenPwned API to check if emails or passwords have been compromised.}
            \resumeItem{Implemented user authentication with hashed passwords and managed data using SQLite databases.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Nike Store} -- \emph{Inventory management system} $|$ \textbf{C\#, Windows Forms, MSSQL}}{\href{https://github.com/MianSaadTahir/nike-store}{Source Code}}
          \resumeItemListStart
            \resumeItem{Developed a Win Forms POS system with SQL database for inventory control and customer order management.}
            \resumeItem{Implemented a modular 3-tier architecture with separate business logic, data access, and UI layers for scalability.}
            \resumeItem{Implemented object-oriented programming practices such as inheritance to create different account types and databases.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
                    \resumeProjectHeading
              {\textbf{Video Nexus} -- \emph{Video entertainment platform} $|$ \textbf{HTML, CSS, JavaScript}}{\href{https://videonexus.netlify.app/}{Live Preview}}
          \resumeItemListStart
            \resumeItem{Built a web video platform that allows users to browse and play content across multiple categories.}
            \resumeItem{Designed a clean, responsive frontend with custom playback controls using vanilla JavaScript.}

          \resumeItemListEnd 
          \vspace{-13pt}
                              \resumeProjectHeading
              {\textbf{Escape Plan} -- \emph{2D GUI shooter game} $|$ \textbf{C\#, Windows Forms}}{\href{https://github.com/MianSaadTahir/Escape-Plan}{Source Code}}
          \resumeItemListStart
            \resumeItem{Developed a Windows-Forms based tank battlefield game showcasing dynamic movement and firing mechanics.}
            \resumeItem{Designed modular DLL architecture and implemented key OOP principles including Interfaces, Singleton, and Enums.}
            \resumeItem{Built gameplay features like real-time player control, enemy tanks, final boss plane, health system and collisions.}
          \resumeItemListEnd 
          \vspace{-10pt}
          
    \resumeSubHeadingListEnd
\vspace{-5pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Languages}{: Python, C\#, C++, SQL, JavaScript, HTML, CSS} \\
    \textbf{Developer Tools}{: VS Code, Git, Jupyter, Colab, Arduino IDE} \\
    \textbf{Libraries / Frameworks}{: TensorFlow, Keras, Flask, Scikit-Learn, Pandas, MSSQL, WinForms, Jinja2}
  }}
\end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Codex 2.0}{Nov. 2023}{Coding Competition Participant}{UET Lahore}
            \resumeItemListStart
                \resumeItem{Participated in problem-solving rounds hosted by Software Square Society}
                \resumeItem{Successfully solved 2 out of 3 problems in a time-constrained, team-based competition.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
